### 2016-12-18 paper/chapters/vae.tex
added reconstruction and samples for MNIST@VAE

\begin{figure}[h!]
\centering
%\resizebox{5cm}{!}{\input{media/vae_architecture.tikz}}
\includegraphics{media/manifold.pdf}
  \caption{MNIST 2-dimensional manifold}\label{fig:vae_manifold}
  \medskip
  \small
  Manifold learned by a VAE using a 2-dimensional latent space for $z \in [-3,3]^2$.
\end{figure}

>>>>

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[height=7cm]{media/vae_manifold-crop.pdf}
        \caption{Learned manifold using 2-dimensional latent space}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[height=7cm]{media/vae_samples-crop.pdf}
        \caption{generated images by sampling from latent space and applying $p(x|z)$}
    \end{subfigure}
    \caption{Variational autoencoder learning performance}
\end{figure*}
